How to be a good member of a scientific software community [Article v\versionnumber]

### 2021-06-09 templates/paper.tex
removed some boilerplate

\section{Checklists}
Training articles do not necessarily require the use of a checklist as in Best Practices documents; however, they can include these if desired.
Several useful checklist formats are available, with examples presented in \texttt{sample-document.tex} in \url{github.com/livecomsjournal/article_templates/templates}.
One example is shown here.

% Here is a single-column checklist that consists of multiple sub-checklists
\begin{Checklists}

>>>>

\section{Checklists}
% Here is a single-column checklist that consists of multiple sub-checklists
\begin{Checklists}
